---
title: "Dr. Paul Schmidt's CV"
author:
  firstname: Dr. Paul
  lastname: Schmidt
  address: "Hamburg, Germany"
  position: "Data Scientist / Biostatistician"
  contacts:
    - icon: fa envelope
      text: schmidtpaul1989@outlook.com
      url: "mailto:schmidtpaul1989@outlook.com"
    - icon: fa phone
      text: +49 172 3091577
      url: "tel:+491723091577"
    - icon: fa brands linkedin
      text: schmidtpaul1989
      url: "https://www.linkedin.com/in/schmidtpaul1989/"
    - icon: fa brands github
      text: SchmidtPaul
      url: "https://github.com/SchmidtPaul/"
    - icon: fa globe
      text: schmidtpaul.github.io
      url: "https://schmidtpaul.github.io/"
    - icon: fa pencil-square
      text: ResearchGate
      url: "https://www.researchgate.net/profile/Paul_Schmidt17"
format:
  typst:
    template-partials:
      - src/awesomecv/typst-show.typ
      - src/awesomecv/typst-template.typ
    toc: true
keep-typ: false
brand:
  typography:
    base: Arial # Source Sans 3
  color:
    primary: "#00923f"
    link: "#00923f"
  defaults:
    awesomecv-typst:
      font-header: Arial # Roboto
profile-photo: "img/paulzoomcircle.png"
bibliography: "CV/citavi_publications.bib"
# csl: src/apa.csl
link-citations: true
citeproc: true
nocite: '@*'
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
library(here)
library(typstcv)
source(here("CV", "CVhelper-typst.R"))
cv <- readRDS(here("CV", "CV_ready.rds"))
```

# Professional Experience

My primary position is Data Scientist and General Manager at BioMath GmbH. Since April 2026 I additionally hold a 25 % position as research associate at the University of Hohenheim (Biostatistics Unit, Prof. Hans-Peter Piepho) within the DFG Research Unit FOR 6101 "MultiStress". I also teach statistics workshops on a freelance basis (see *Workshops* section).

```{r}
#| output: asis
cv_emit_experience("eng")
```

```{=typst}
#pagebreak(weak: true)
```

# Education

```{r}
#| output: asis
cv_emit_education("eng")
```

# Skills

```{r}
#| output: asis
cv_emit_skills("eng")
```

```{=typst}
#pagebreak(weak: true)
```

# Favorite R Packages

```{=typst}
#import "@preview/fontawesome:0.5.0": *
#let ic(n) = text(fill: rgb("#00923f"), size: 0.72em, baseline: -0.1em)[#fa-icon(n)]
#let p(name, url) = link(url)[#name]

#text(size: 0.8em, style: "italic")[
  #ic("pen-nib") Author #h(0.7em) #ic("user-pen") Co-author #h(0.7em) #ic("code-pull-request") Contributor #h(0.7em) #ic("heart") heavy user
]

#v(0.35em)

#text(weight: "bold")[Experimental design & field trials:] #p("desplot", "https://kwstat.github.io/desplot/") #ic("user-pen"), #p("FielDHub", "https://didiermurillof.github.io/FielDHub/") #ic("code-pull-request"), #p("agridat", "https://kwstat.github.io/agridat/") #ic("code-pull-request")

#text(weight: "bold")[Mixed models & inference:] #p("lme4", "https://github.com/lme4/lme4") #ic("heart"), #p("glmmTMB", "https://glmmtmb.github.io/glmmTMB/") #ic("code-pull-request"), #p("emmeans", "https://rvlenth.github.io/emmeans/") #ic("code-pull-request"), #p("easystats", "https://easystats.github.io/easystats/") #ic("heart"), #p("heritable", "https://anu-aagi.github.io/heritable/") #ic("code-pull-request")

#text(weight: "bold")[Reporting & reproducibility:] #p("quarto", "https://quarto.org/") #ic("heart"), #p("targets", "https://docs.ropensci.org/targets/") #ic("heart"), #p("openxlsx2", "https://janmarvin.github.io/openxlsx2/") #ic("code-pull-request"), #p("officer", "https://davidgohel.github.io/officer/") + #p("officedown", "https://davidgohel.github.io/officedown/") #ic("heart"), #p("excelcompare", "https://github.com/SchmidtPaul/excelcompare") #ic("pen-nib"), #p("BioMathR", "https://schmidtpaul.github.io/BioMathR/") #ic("pen-nib")

#text(weight: "bold")[Data wrangling & visualization:] #p("tidyverse", "https://www.tidyverse.org/") #ic("heart"), #p("ggplot2", "https://ggplot2.tidyverse.org/") + #p("ggtext", "https://wilkelab.org/ggtext/") + #p("ggrepel", "https://ggrepel.slowkow.com/") + #p("patchwork", "https://patchwork.data-imaginist.com/") #ic("heart")
```

# Workshops

```{r}
#| output: asis
cv_emit_workshops()
```

# Publications

::: {#refs}
:::
